Fixing Vulnerabilities Hinders Maintainability

### 2019-02-01 paper/ICPC19/icpc19.tex
clarifying what OpenSSL is

This paper is structured as follows: section \ref{sec:motivation} introduces an
example of a security refactoring of a known vulnerability found in
OpenSSL\footnote{Repository available at https://github.com/openssl/openssl
(Accessed on \today{})} software; section \ref{sec:methodology} describes the
methodology used to answer the research questions; section \ref{sec:results}
presents the results and section \ref{sec:discussion} discusses their
implications; section \ref{sec:threats}, threats to the validity of the study
are enumerated; section \ref{sec:rw} describres the different work and existing
literature in the field of study; and, finally section \ref{sec:conclusions}
concludes the main findings and elaborates on future work.
%
\section{Motivation and Research Questions}\label{sec:motivation}
%
Due to time-to-market pressure and the lack of security expertise, code-related
security flaws are generally detected \textit{after the fact}, i.e., when
hackers exploit them. It turns out that fixing these issues is as simple as
modifying the software codebase. However, these refactorings may have a negative
impact on software maintenance, mostly because developers follow the quickest
solution to fix the problem and not necessarily the most elegant and performant
one. Thus, we want to understand how security refactorings impact the
maintainability of software.

As an example, consider the refactoring of the Datagram Transport Layer Security
(DTLS) protocol implementation in OpenSSL to address the fact that hackers could
cause a Denial-of-Service (DoS) attack by crafting DTLS
handshake messages to trigger memory allocations corresponding to large length
values. This vulnerability is listed at the Common Vulnerabilities and Exposures
dictionary as CVE-2014-3506\footnote{CVE-2014-3506 details available at
http://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2014-3506 (Accessed on
\today{})}. It is amongst the vulnerabilities studied in our evaluation.
The following snippet presents the changes performend on the
\emph{ssl/d1\_both.c} file\footnote{CVE-2014-3506 fix available  at
https://github.com/openssl/openssl/commit/\\1250f12613b61758675848f6600ebd914ccd7636
(Accessed on \today{})} by the OpenSLL developers to fix the vulnerability.

>>>>

This paper is structured as follows: section \ref{sec:motivation} introduces an
example of a security refactoring of a known vulnerability found in
OpenSSL\footnote{Repository available at https://github.com/openssl/openssl
(Accessed on \today{})}; section \ref{sec:methodology} describes the
methodology used to answer the research questions; section \ref{sec:results}
presents the results and section \ref{sec:discussion} discusses their
implications; section \ref{sec:threats}, threats to the validity of the study
are enumerated; section \ref{sec:rw} describres the different work and existing
literature in the field of study; and, finally section \ref{sec:conclusions}
concludes the main findings and elaborates on future work.
%
\section{Motivation and Research Questions}\label{sec:motivation}
%
Due to time-to-market pressure and the lack of security expertise, code-related
security flaws are generally detected \textit{after the fact}, i.e., when
hackers exploit them. It turns out that fixing these issues is as simple as
modifying the software codebase. However, these refactorings may have a negative
impact on software maintenance, mostly because developers follow the quickest
solution to fix the problem and not necessarily the most elegant and performant
one. Thus, we want to understand how security refactorings impact the
maintainability of software.

As an example, consider the refactoring of the Datagram Transport Layer Security
(DTLS) protocol implementation in OpenSSL\footnote{OpenSSL is a tookit that
contains open-source implementations of the SSL and TLS cryptographic
protocols.} to address the fact that hackers could cause a Denial-of-Service
(DoS) attack by crafting DTLS handshake messages to trigger memory allocations
corresponding to large length values. This vulnerability is listed at the Common
Vulnerabilities and Exposures dictionary as CVE-2014-3506\footnote{CVE-2014-3506
details available at http://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2014-3506
(Accessed on \today{})}. It is amongst the vulnerabilities studied in our
evaluation. The following snippet presents the changes performend on the
\emph{ssl/d1\_both.c} file\footnote{CVE-2014-3506 fix available  at
https://github.com/openssl/openssl/commit/\\1250f12613b61758675848f6600ebd914ccd7636
(Accessed on \today{})} by the OpenSLL developers to fix the vulnerability.
